---
title: "Final_Project"
author: "Group K"
date: '2022-06-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(readxl)
```

```{r}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/ggpubr")
```

```{r}
library(cowplot)
```


```{r}
file_location_post = #Here put the link for the Post Excel 
file_location_pre = #Here put the link for the Pre Excel 
post = read_excel(file_location_post)
pre = read_excel(file_location_pre)
```

```{r}
post_row_num = nrow(post) # number of students POST 
pre_row_num = nrow(pre) # number of students PRE
```

#graph that shows the amount of students divide by gender
```{r}
pr_gender = pre %>% 
  group_by(gender) %>%
  count(gender)

ggplot(pr_gender, aes(x=gender, y=n, fill = gender)) +
  geom_bar(stat="identity", position="dodge") +  
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25)
 
```

#graph that shows the amount of students divide by teachers
```{r}
po_gender = post %>% 
  group_by(teacher) %>%
  count(teacher)


ggplot(po_gender, aes(x=teacher, y=n, fill = teacher)) +
  geom_bar(stat="identity", position="dodge") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25)

```

#change all the 0.5 values in the Agree/Disagree questions to Abstainers
```{r}
post$three_a[post$three_a == "0.5"] <- "abstainers"    
pre$two_a[pre$two_a == "0.5"] <- "abstainers"    

post$three_c[post$three_c == "0.5"] <- "abstainers"    
pre$two_c[pre$two_c == "0.5"] <- "abstainers"    
```

#making graph for questions 3a 
```{r}
po_three_a = post %>% 
  group_by(three_a) %>%
  count(three_a) %>%
  mutate(percentage = n * 100/post_row_num) %>%
  mutate(pre_or_post = 1)

#df_pre = df_pre %>% 
#  mutate(pre_or_post = 1)

pr_two_a = pre %>% 
  group_by(two_a) %>%
  count(two_a) %>%
  mutate(percentage = n * 100/pre_row_num) %>%
  mutate(pre_or_post = 0)
  
colnames(po_three_a) <- c('q','n','percentage', 'pre_or_post') # change coloum names for union
colnames(pr_two_a) <- c('q','n','percentage','pre_or_post') # change coloumn names for union

x_labels <- c("Disagree", "Agree", "Abstainers")
facet_name <- c('0' = "Pre Reasearch",'1' = "Post Reasearch")

po_pr_two_a <- union(pr_two_a, po_three_a)  #combine the to data frames

plot_two_a = ggplot(po_pr_two_a, aes(q, percentage,fill = q)) + 
  geom_bar(stat = "identity", position="dodge") +
  labs(title = "Does Science Interest Me?",x = 'Teacher', y = 'Percentage')+
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  facet_grid(cols = vars(pre_or_post), labeller = as_labeller(facet_name)) +
  scale_x_discrete(labels= x_labels)+
  theme(legend.position = "none")

plot_two_a

```

#making graph for questions 3c
```{r}
po_three_c = post %>% 
  group_by(three_c) %>%
  count(three_c) %>%
  mutate(percentage = n * 100/post_row_num) %>%
  mutate(pre_or_post = 1)

pr_two_c = pre %>% 
  group_by(two_c) %>%
  count(two_c) %>%
  mutate(percentage = n * 100/pre_row_num) %>%
  mutate(pre_or_post = 0)

colnames(po_three_c) <- c('q','n','percentage', 'pre_or_post') # change coloum names for union
colnames(pr_two_c) <- c('q','n','percentage','pre_or_post')

po_pr_two_c <- union(pr_two_c, po_three_c)  # combine the two df's

plot_two_c = ggplot(po_pr_two_c, aes(q, percentage,fill = q)) + 
  geom_bar(stat = "identity", position="dodge") + 
  labs(title = "Science Is Important To Me?",x = 'Teacher', y = 'Percentage') +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  scale_x_discrete(labels= x_labels) +
  facet_grid(cols = vars(pre_or_post), labeller = as_labeller(facet_name))+
  theme(legend.position = "none")
plot_two_c
```

#plot 3a and 3c using cowplot 
#NOTE: this plot uses cowplot library to combine th two plots to one, not neccessry.  
```{r}
plot_grid(plot_two_a,plot_two_c, labels = "AUTO") #using the cowplot library, show the 2 graph's in one 
```

now i would like to make similar graph too explain the previous result, ill create a plot by teacher 
```{r}
po_three_a_teacher = post %>% 
  group_by(three_a,teacher) %>%
  count(three_a) %>%
  mutate(percentage = round((n * 100)/post_row_num,2)) %>%
  mutate(pre_or_post = 1)

pr_two_a_teacher = pre %>% 
  group_by(two_a,teacher) %>%
  count(two_a) %>%
  mutate(percentage = round((n * 100)/pre_row_num,2)) %>%
  mutate(pre_or_post = 0)

colnames(po_three_a_teacher) <- c('q','teacher','n','percentage', 'pre_or_post')
colnames(pr_two_a_teacher) <- c('q','teacher','n','percentage', 'pre_or_post')

```

#i want to show the percentage per teacher and for that i need the number of students for each #teacher that answered 3a before the experiment and after.

#this block of code is for calculating the amount of students per teacher Post experiment
```{r}
#get all the number of students from all teacher Post
po_three_a_An = po_three_a_teacher %>%
  filter(teacher == "An")
An_count_po = sum(po_three_a_An$n)
po_three_a_An = po_three_a_An %>%
  mutate(class_percentage = round(n*100/An_count_po,1))

po_three_a_Av = po_three_a_teacher %>%
  filter(teacher == "Av")
Av_count_po = sum(po_three_a_Av$n)
po_three_a_Av = po_three_a_Av %>%
  mutate(class_percentage = round(n*100/Av_count_po,1))


po_three_a_Ga = po_three_a_teacher %>%
  filter(teacher == "Ga")
Ga_count_po = sum(po_three_a_Ga$n)
po_three_a_Ga = po_three_a_Ga %>%
  mutate(class_percentage = round(n*100/Ga_count_po,1))


po_three_a_Ke = po_three_a_teacher %>%
  filter(teacher == "Ke")
Ke_count_po = sum(po_three_a_Ke$n)
po_three_a_Ke = po_three_a_Ke %>%
  mutate(class_percentage = round(n*100/Ke_count_po,1))


po_three_a_Mo = po_three_a_teacher %>%
  filter(teacher == "Mo")
Mo_count_po = sum(po_three_a_Mo$n)
po_three_a_Mo = po_three_a_Mo %>%
  mutate(class_percentage = round(n*100/Mo_count_po,1))


po_three_a_Na = po_three_a_teacher %>%
  filter(teacher == "Na")
Na_count_po = sum(po_three_a_Na$n)
po_three_a_Na = po_three_a_Na %>%
  mutate(class_percentage = round(n*100/Na_count_po,1))

```

#this block of code is for calculating the amount of students per teacher Pre experiment
```{r}
#get all the number of students from all teacher PRE
pr_two_a_An = pr_two_a_teacher %>%
  filter(teacher == "An")
An_count_pre = sum(pr_two_a_An$n)
pr_two_a_An = pr_two_a_An %>%
  mutate(class_percentage = round(n*100/An_count_pre,1))

pr_two_a_Av = pr_two_a_teacher %>%
  filter(teacher == "Av")
Av_count_pre = sum(pr_two_a_Av$n)
pr_two_a_Av = pr_two_a_Av %>%
  mutate(class_percentage = round(n*100/Av_count_pre,1))


pr_two_a_Ga = pr_two_a_teacher %>%
  filter(teacher == "Ga")
Ga_count_pre = sum(pr_two_a_Ga$n)
pr_two_a_Ga = pr_two_a_Ga %>%
  mutate(class_percentage = round(n*100/Ga_count_pre,1))

pr_two_a_Ke = pr_two_a_teacher %>%
  filter(teacher == "Ke")
Ke_count_pre = sum(pr_two_a_Ke$n)
pr_two_a_Ke = pr_two_a_Ke %>%
  mutate(class_percentage = round(n*100/Ke_count_pre,1))


pr_two_a_Mo = pr_two_a_teacher %>%
  filter(teacher == "Mo")
Mo_count_pre = sum(pr_two_a_Mo$n)
pr_two_a_Mo = pr_two_a_Mo %>%
  mutate(class_percentage = round(n*100/Mo_count_pre,1))


pr_two_a_Na = pr_two_a_teacher %>%
  filter(teacher == "Na")
Na_count_pre = sum(pr_two_a_Na$n)
pr_two_a_Na = pr_two_a_Na %>%
  mutate(class_percentage = round(n*100/Na_count_pre,1))
```


```{r} 
#combine all the teacher based tables with there currect presentage per teacher
po_three_a_teacher_percentage <- bind_rows(po_three_a_An, po_three_a_Av, po_three_a_Ga, po_three_a_Ke, po_three_a_Mo, po_three_a_Na)

pr_three_a_teacher_percentage <- bind_rows(pr_two_a_An, pr_two_a_Av, pr_two_a_Ga, pr_two_a_Ke, pr_two_a_Mo, pr_two_a_Na)

po_pr_two_a_teacher_percentage <- union(po_three_a_teacher_percentage, pr_three_a_teacher_percentage)  

```

#plot first graph, does scince interest me?
```{r}
  ggplot(po_pr_two_a_teacher_percentage, aes(teacher, class_percentage,fill = q)) + 
  geom_bar(stat = "identity", position="dodge") + 
  labs(title = "Does Science Interest Me?",x = 'Teacher', y = 'Percentage', fill= 'Disagree / Agree') +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  facet_grid(cols = vars(pre_or_post), labeller = as_labeller(facet_name))+
  #theme(legend.position = "none") +
  geom_text(aes(label=class_percentage), position=position_dodge(width=1), vjust=-0.25,size = 2.1)

```

#i want to show the percentage per teacher and for that i need the number of students for each #teacher that answered 3c before the experiment and after.
```{r}

po_three_c_teacher = post %>% 
  group_by(three_c,teacher) %>%
  count(three_c) %>%
  mutate(percentage = round((n * 100)/post_row_num,2)) %>%
  mutate(pre_or_post = 1)

pr_two_c_teacher = pre %>% 
  group_by(two_c,teacher) %>%
  count(two_c) %>%
  mutate(percentage = round((n * 100)/pre_row_num,2)) %>%
  mutate(pre_or_post = 0)

colnames(po_three_c_teacher) <- c('q','teacher','n','percentage', 'pre_or_post')
colnames(pr_two_c_teacher) <- c('q','teacher','n','percentage', 'pre_or_post')

```

#this block of code is for calculating the amount of students per teacher Post experiment
```{r}
#get all the number of students from all teacher Post
po_three_c_An = po_three_c_teacher %>%
  filter(teacher == "An")
An_count_po = sum(po_three_c_An$n)
po_three_c_An = po_three_c_An %>%
  mutate(class_percentage = round(n*100/An_count_po,1))

po_three_c_Av = po_three_c_teacher %>%
  filter(teacher == "Av")
Av_count_po = sum(po_three_c_Av$n)
po_three_c_Av = po_three_c_Av %>%
  mutate(class_percentage = round(n*100/Av_count_po,1))


po_three_c_Ga = po_three_c_teacher %>%
  filter(teacher == "Ga")
Ga_count_po = sum(po_three_c_Ga$n)
po_three_c_Ga = po_three_c_Ga %>%
  mutate(class_percentage = round(n*100/Ga_count_po,1))

po_three_c_Ke = po_three_c_teacher %>%
  filter(teacher == "Ke")
Ke_count_po = sum(po_three_c_Ke$n)
po_three_c_Ke = po_three_c_Ke %>%
  mutate(class_percentage = round(n*100/Ke_count_po,1))


po_three_c_Mo = po_three_c_teacher %>%
  filter(teacher == "Mo")
Mo_count_po = sum(po_three_c_Mo$n)
po_three_c_Mo = po_three_c_Mo %>%
  mutate(class_percentage = round(n*100/Mo_count_po,1))


po_three_c_Na = po_three_c_teacher %>%
  filter(teacher == "Na")
Na_count_po = sum(po_three_c_Na$n)
po_three_c_Na = po_three_c_Na %>%
  mutate(class_percentage = round(n*100/Na_count_po,1))

```

#this block of code is for calculating the amount of students per teacher Pre experiment
```{r}
#get all the number of students from all teacher PRE
pr_two_c_An = pr_two_c_teacher %>%
  filter(teacher == "An")
An_count_pre = sum(pr_two_c_An$n)
pr_two_c_An = pr_two_c_An %>%
  mutate(class_percentage = round(n*100/An_count_pre,1))

pr_two_c_Av = pr_two_c_teacher %>%
  filter(teacher == "Av")
Av_count_pre = sum(pr_two_c_Av$n)
pr_two_c_Av = pr_two_c_Av %>%
  mutate(class_percentage = round(n*100/Av_count_pre,1))


pr_two_c_Ga = pr_two_c_teacher %>%
  filter(teacher == "Ga")
Ga_count_pre = sum(pr_two_c_Ga$n)
pr_two_c_Ga = pr_two_c_Ga %>%
  mutate(class_percentage = round(n*100/Ga_count_pre,1))

pr_two_c_Ke = pr_two_c_teacher %>%
  filter(teacher == "Ke")
Ke_count_pre = sum(pr_two_c_Ke$n)
pr_two_c_Ke = pr_two_c_Ke %>%
  mutate(class_percentage = round(n*100/Ke_count_pre,1))


pr_two_c_Mo = pr_two_c_teacher %>%
  filter(teacher == "Mo")
Mo_count_pre = sum(pr_two_c_Mo$n)
pr_two_c_Mo = pr_two_c_Mo %>%
  mutate(class_percentage = round(n*100/Mo_count_pre,1))

pr_two_c_Na = pr_two_c_teacher %>%
  filter(teacher == "Na")
Na_count_pre = sum(pr_two_c_Na$n)
pr_two_c_Na = pr_two_c_Na %>%
  mutate(class_percentage = round(n*100/Na_count_pre,1))
```

```{r} 
#combine all the teacher based tables
po_three_c_teacher_percentage <- bind_rows(po_three_c_An, po_three_c_Av, po_three_c_Ga, po_three_c_Ke, po_three_c_Mo, po_three_c_Na)

pr_three_c_teacher_percentage <- bind_rows(pr_two_c_An, pr_two_c_Av, pr_two_c_Ga, pr_two_c_Ke, pr_two_c_Mo, pr_two_c_Na)

po_pr_two_c_teacher_percentage <- union(po_three_c_teacher_percentage, pr_three_c_teacher_percentage)  
```

#plot 3c graph, science is important to me

```{r}
  ggplot(po_pr_two_c_teacher_percentage, aes(teacher, class_percentage,fill = q)) + 
  geom_bar(stat = "identity", position="dodge") + 
  labs(title = "Science Is Important To Me?",x = 'Teacher', y = 'Percentage' ,fill = "Disagree/ Agree") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1)) +
  facet_grid(cols = vars(pre_or_post), labeller = as_labeller(facet_name))+
  #theme(legend.position = "none") +
  geom_text(aes(label=class_percentage), position=position_dodge(width=1), vjust=-0.25,size = 2.1)

```


##########################################################################
# Create a data frame with the mean change of questions b,c,d  of all the teachers

```{r pressure, echo=FALSE}

#(5 Post)4 פרי ב,ג,ד,ו

a <- c(0)
b <- c(0)
m <- c(0)
t <- c("har")
q <- c("ha")
df <- data.frame(b,a,m,t,q)


#Calculates the average of the changes of the answers before and after in a particular question
meananscalc <- function(qupre,qupost, teachpre,teachpost,nameteach,qu) {
bb=mean(as.numeric(qupre[qupre!="abstainers"][teachpre==nameteach]), na.rm = TRUE)
aa=mean(as.numeric(qupost[qupost!="abstainers"][teachpost==nameteach]), na.rm = TRUE)
my2.vec <- c(round(bb,digits = 3),round(aa,digits = 3),round(aa-bb,digits = 3),nameteach,qu)
my2.vec
  }

ca=c("Ke","An","Av","Ga","Mo","Na")
for (i in ca){
  vec2=meananscalc(pre$four_b,post$five_b,pre$teacher,post$teacher,i,"A")
  vec3=meananscalc(pre$four_c,post$five_c,pre$teacher,post$teacher,i,"B")
  vec4=meananscalc(pre$four_d,post$five_d,pre$teacher,post$teacher,i,"C")
  df <- rbind(df,vec2,vec3,vec4)

}
df=df[-c(1),]
df$b <- as.numeric(df$b)
df$a <- as.numeric(df$a)
df$m <- as.numeric(df$m)

dfm=df %>%
  filter(t!="Na") %>%
  filter(t!="Mo")


dft=df %>%
  filter(t!="Ke") %>%
  filter(t!="An") %>%
  filter(t!="Av") %>%
  filter(t!="Ga")
```
#plot The average change in student responses by class
```{r}

ggplot(dfm,aes(x=q, y=m,fill=t, color=t))+
geom_bar(stat = "identity", position = "dodge")+
  labs(x="Question",y="The average change in student responses" , color="Elementry school teacher",fill="Elementry school teacher", title =" Elementary School" ,subtitle ="A - It's important to learn science even if it's not your occupation\nB - My science knowledge helps me in day-to-day life.\nC - Science helps to explain world phenomenon" )


ggplot(dft,aes(x=q, y=m,fill=t, color=t))+
geom_bar(stat = "identity", position = "dodge")+
  labs(x="Question",y="The average change in student responses" , color="Midlle school teacher",fill="Midlle school teacher",title =" Middle School" ,subtitle ="A - It's important to learn science even if it's not your occupation\nB - My science knowledge helps me in day-to-day life.\nC - Science helps to explain world phenomenon")


```
#creates a data frame of "tet"(ט) grade students with there answers for question c before and after the experiment
```{r,echo = TRUE}
 

postt=post %>%
  filter(class=="tet")
pret=pre %>%
  filter(class=="tet")

dfpo=data.frame(postt$student_id,postt$five_c)
dfpre=data.frame(pret$student_id,pret$four_c)


combined=merge(dfpo,dfpre,by.x = "postt.student_id",by.y ="pret.student_id" )
combined$postt.five_c <- as.numeric((combined$postt.five_c))
combined$pret.four_c <- as.numeric((combined$pret.four_c))


combined$postt.five_c[is.na(combined$postt.five_c)] <- mean(combined$postt.five_c, na.rm = TRUE)
combined$pret.four_c[is.na(combined$pret.four_c)] <- mean(combined$pret.four_c, na.rm = TRUE)
```


#creates a linear regression model of this data frame
```{r,echo = TRUE}
cor(combined$pret.four_c,combined$postt.five_c)
ggplot(combined,aes(pret.four_c,postt.five_c)) +
  geom_point() +
  geom_smooth(method='lm')+
labs(x="Pre answer",y="Post answer", title = "Linear Regression Of The Pre And Post Experiment Answers For The Question" )
```

#create a function that predict the post answer of a student by applying linear regression modlle using his pre answer and his teacher

```{r}
predict_score_by_teacher<-function(teach,pre_qustion,post_qustion,pre_ans_of_the_kid){
 
  dfpo=data.frame(post$student_id,post_qustion,post$teacher)
  dfpre=data.frame(pre$student_id,pre_qustion,pre$teacher)
 
  postt=dfpo %>%
    filter(post.teacher==teach)
  pret=dfpre %>%
    filter(pre.teacher==teach)
 
 
 combined=merge(postt,pret,by.x = "post.student_id",by.y ="pre.student_id" )

  combined[, c(2)] <- as.numeric((combined[, c(2)]))
  combined[, c(4)] <- as.numeric((combined[, c(4)]))
 
  combined$post_qustion[is.na(combined$post_qustion)] <- mean(combined$post_qustion, na.rm = TRUE)
  combined$pre_qustion[is.na(combined$pre_qustion)] <- mean(combined$pre_qustion, na.rm = TRUE)
 
 
  r=lm( post_qustion~ pre_qustion,data = combined)
  summary(r)
 
  xxx=coef(r)[1]+coef(r)[2]*pre_ans_of_the_kid
  as.numeric(xxx)
}

#EXMPLE OF HOW TO USE THE PREDICT MODLE: PRDICT BY TEACHER
predict_score_by_teacher("Mo",pre$two_a,post$three_a,1)

```
##this code shows an example of how well the modle fits by the r squred test.
#in this particular example we get 0.65 out of 1.
```{r}
  dfpo=data.frame(post$student_id,post$five_c,post$teacher)
  dfpre=data.frame(pre$student_id,pre$four_c,pre$teacher)
 
  postt=dfpo %>%
    filter(post.teacher=="Mo")
  pret=dfpre %>%
    filter(pre.teacher=="Mo")
 
 
 combined=merge(postt,pret,by.x = "post.student_id",by.y ="pre.student_id" )

  combined[, c(2)] <- as.numeric((combined[, c(2)]))
  combined[, c(4)] <- as.numeric((combined[, c(4)]))
 
  combined$post.five_c[is.na(combined$post.five_c)] <- mean(combined$post.five_c, na.rm = TRUE)
  combined$pre.four_c[is.na(combined$pre.four_c)] <- mean(combined$pre.four_c, na.rm = TRUE)
  
 
  rr=lm( combined$post.five_c~ pre.four_c,data = combined)
  summary(rr)$r.squared
```


# A graph which shows the middle school rankings for the question "How much do you know about the following topics?"

```{r}

#make numeric
post$six_b_af <- as.numeric(post$six_b_af)
post$six_c_af <- as.numeric(post$six_c_af)

#count 5b
pre_sch_count_5b <- pre %>% filter(class =='tet') %>% drop_na(five_b) %>% count(five_b, name = 'count_5b_pre')
post_sch_count_5b  <- post %>% filter(class =='tet') %>% drop_na(six_b_af)  %>% count(six_b_af, name = 'count_6b_post')

## count -> precentage
pre_sch_count_5b$prop_5b_pre <- pre_sch_count_5b$count_5b_pre / sum(pre_sch_count_5b$count_5b_pre)
post_sch_count_5b$prop_5b_post <- post_sch_count_5b$count_6b_post/ sum(post_sch_count_5b$count_6b_post)

#count 5c
pre_sch_count_5c <- pre %>% filter(class =='tet') %>% drop_na(five_c) %>% count(five_c, name = 'count_5c_pre')
post_sch_count_5c  <- post %>% filter(class =='tet') %>% drop_na(six_c_af)  %>% count(six_c_af, name = 'count_6c_post')


## count -> precentage
pre_sch_count_5c$prop_5c_pre <- pre_sch_count_5c$count_5c_pre / sum(pre_sch_count_5c$count_5c_pre)
post_sch_count_5c$prop_5c_post <- post_sch_count_5c$count_6c_post / sum(post_sch_count_5c$count_6c_post)


#change col names
colnames(pre_sch_count_5b) <- c("range", "5b_pre", "5b_pre_prop")
colnames(post_sch_count_5b) <- c("range", "5b_post", "5b_post_prop")



#union & change NA to 0
## 5b

df_5b <- merge(x=pre_sch_count_5b,y=post_sch_count_5b,by=c("range"),all.x =TRUE)

df_5b$`5b_pre`[is.na(df_5b$`5b_pre`)] <- 0
df_5b$`5b_post`[is.na(df_5b$`5b_post`)] <- 0


df_5b_prop <- df_5b %>% select(1,3,5)
df_5b_prop$`5b_pre_prop`[is.na(df_5b_prop$`5b_pre_prop`)] <- 0
df_5b_prop$`5b_post_prop`[is.na(df_5b_prop$`5b_post_prop`)] <- 0
df_5b_prop

#reshape the data
 df_5b_prop_long <- df_5b_prop %>%
 gather(key = "question", value = "value", -range)


df_b_pre <- filter( df_5b_prop_long, question == "5b_pre_prop")
df_b_pre <- df_b_pre %>%
  mutate(when = "Pre")

df_b_post <- filter( df_5b_prop_long, question == "5b_post_prop")
df_b_post <- df_b_post %>%
  mutate(when = "Post")

df_5b_prop <- union(df_b_pre, df_b_post) %>% mutate(section = "A")
df_5b_prop$range <- as.double(df_5b_prop$range)


#make numeric

#count 5c
pre_sch_count_5c <- pre %>% filter(class =='tet') %>% drop_na(five_c) %>% count(five_c, name = 'count_5c_pre')
post_sch_count_5c  <- post %>% filter(class =='tet') %>% drop_na(six_c_af)  %>% count(six_c_af, name = 'count_6c_post')

pre_sch_count_5c


## count -> precentage
pre_sch_count_5c$prop_5c_pre <- pre_sch_count_5c$count_5c_pre / sum(pre_sch_count_5c$count_5c_pre)
post_sch_count_5c$prop_5c_post <- post_sch_count_5c$count_6c_post / sum(post_sch_count_5c$count_6c_post)


#change col names
colnames(pre_sch_count_5c) <- c("range", "5c_pre", "5c_pre_prop")
colnames(post_sch_count_5c) <- c("range", "5c_post", "5c_post_prop")


#union & change NA to 0

##5c
df_5c <- merge(x=post_sch_count_5c,y=pre_sch_count_5c,by="range",all.x=TRUE)
df_5c$`5c_pre`[is.na(df_5c$`5c_pre`)] <- 0
df_5c$`5c_post`[is.na(df_5c$`5c_post`)] <- 0

df_5c_prop <- df_5c %>% select(1,3,5)
df_5c_prop$`5c_pre_prop`[is.na(df_5c_prop$`5c_pre_prop`)] <- 0
df_5c_prop$`5c_post_prop`[is.na(df_5c_prop$`5c_post_prop`)] <- 0

#reshape the data
 df_5c_prop_long <- df_5c_prop %>%
 gather(key = "question", value = "value", -range)
 
 
df_c_pre <- filter( df_5c_prop_long, question == "5c_pre_prop")
df_c_pre <- df_c_pre %>%
  mutate(when = "Pre")

df_c_post <- filter( df_5c_prop_long, question == "5c_post_prop")
df_c_post <- df_c_post %>%
  mutate(when = "Post")

df_5c_prop <- union(df_c_pre, df_c_post) %>% mutate(section = "B")


df_5 <- union(df_5c_prop, df_5b_prop)

#plot
 ggplot(df_5, aes(x = as.numeric(range), y = value, color = section, linetype = when)) +
  geom_line(size = 1) +
  geom_point(size = 2) + scale_y_continuous(labels = scales::percent_format()) +
     scale_linetype_manual(values=c("solid", "dashed"), labels = c("After", "Before"))+
      scale_color_manual(values=c("#D98E3A", "#A283CD"))+
  labs(x = "Range", y = "Precent")  + theme_light() + labs(color= "Question", linetype= "Before / After", title = "How much do you know about the following topics?", subtitle = "Middle School\nA. Animals in the school environment\nB. How animals in the school environment affect humans")
 
```

# A graph which shows the Elementry school rankings for the question "How much do you know about the following topics?"

```{r}
# Graph for not tet only!!! #
# 5B


#make numeric
post$six_b_af <- as.numeric(post$six_b_af)
post$six_c_af <- as.numeric(post$six_c_af)

#count 5b
pre_sch_count_5b_y <- pre %>% filter(class !='tet' ) %>% drop_na(five_b) %>% count(five_b, name = 'count_5b_pre')
post_sch_count_5b_y  <- post %>% filter(class !='tet' ) %>% drop_na(six_b_af)  %>% count(six_b_af, name = 'count_6b_post')

## count -> precentage
pre_sch_count_5b_y$prop_5b_pre <- pre_sch_count_5b_y$count_5b_pre / sum(pre_sch_count_5b_y$count_5b_pre)
post_sch_count_5b_y$prop_5b_post <- post_sch_count_5b_y$count_6b_post/ sum(post_sch_count_5b_y$count_6b_post)

#count 5c
pre_sch_count_5c_y <- pre %>% filter(class =='tet') %>% drop_na(five_c) %>% count(five_c, name = 'count_5c_pre')
post_sch_count_5c_y  <- post %>% filter(class =='tet') %>% drop_na(six_c_af)  %>% count(six_c_af, name = 'count_6c_post')


## count -> precentage
pre_sch_count_5c_y$prop_5c_pre <- pre_sch_count_5c_y$count_5c_pre / sum(pre_sch_count_5c_y$count_5c_pre)
post_sch_count_5c_y$prop_5c_post <- post_sch_count_5c_y$count_6c_post / sum(post_sch_count_5c_y$count_6c_post)


#change col names
colnames(pre_sch_count_5b_y) <- c("range", "5b_pre", "5b_pre_prop")
colnames(post_sch_count_5b_y) <- c("range", "5b_post", "5b_post_prop")



#union & change NA to 0
## 5b

df_5b <- merge(x=pre_sch_count_5b_y,y=post_sch_count_5b_y,by=c("range"),all.x =TRUE)

df_5b$`5b_pre`[is.na(df_5b$`5b_pre`)] <- 0
df_5b$`5b_post`[is.na(df_5b$`5b_post`)] <- 0


df_5b_prop_y <- df_5b %>% select(1,3,5)
df_5b_prop_y$`5b_pre_prop`[is.na(df_5b_prop$`5b_pre_prop`)] <- 0
df_5b_prop_y$`5b_post_prop`[is.na(df_5b_prop$`5b_post_prop`)] <- 0
df_5b_prop_y

#reshape the data
 df_5b_prop_long_y <- df_5b_prop_y %>%
 gather(key = "question", value = "value", -range)


df_b_pre_y <- filter( df_5b_prop_long_y, question == "5b_pre_prop")
df_b_pre_y <- df_b_pre_y %>%
  mutate(when = "Pre")

df_b_post_y <- filter( df_5b_prop_long_y, question == "5b_post_prop")
df_b_post_y <- df_b_post_y %>%
  mutate(when = "Post")

df_5b_prop_y <- union(df_b_pre_y, df_b_post_y) %>% mutate(section = "A")
df_5b_prop_y$range <- as.double(df_5b_prop_y$range)


#make numeric

#count 5c
pre_sch_count_5c_y <- pre %>% filter(class !='tet') %>% drop_na(five_c) %>% count(five_c, name = 'count_5c_pre')
post_sch_count_5c_y  <- post %>% filter(class !='tet') %>% drop_na(six_c_af)  %>% count(six_c_af, name = 'count_6c_post')



## count -> precentage
pre_sch_count_5c_y$prop_5c_pre <- pre_sch_count_5c_y$count_5c_pre / sum(pre_sch_count_5c_y$count_5c_pre)
post_sch_count_5c_y$prop_5c_post <- post_sch_count_5c_y$count_6c_post / sum(post_sch_count_5c_y$count_6c_post)


#change col names
colnames(pre_sch_count_5c_y) <- c("range", "5c_pre", "5c_pre_prop")
colnames(post_sch_count_5c_y) <- c("range", "5c_post", "5c_post_prop")


#union & change NA to 0

##5c
df_5c_y <- merge(x=post_sch_count_5c_y,y=pre_sch_count_5c_y,by="range",all.x=TRUE)
df_5c_y$`5c_pre`[is.na(df_5c_y$`5c_pre`)] <- 0
df_5c_y$`5c_post`[is.na(df_5c_y$`5c_post`)] <- 0

df_5c_prop_y <- df_5c_y %>% select(1,3,5)
df_5c_prop_y$`5c_pre_prop`[is.na(df_5c_prop_y$`5c_pre_prop`)] <- 0
df_5c_prop_y$`5c_post_prop`[is.na(df_5c_prop_y$`5c_post_prop`)] <- 0

#reshape the data
 df_5c_prop_long_y <- df_5c_prop_y %>%
 gather(key = "question", value = "value", -range)
 
 
df_c_pre_y <- filter( df_5c_prop_long_y, question == "5c_pre_prop")
df_c_pre_y <- df_c_pre_y %>%
  mutate(when = "Pre")

df_c_post_y <- filter( df_5c_prop_long_y, question == "5c_post_prop")
df_c_post_y <- df_c_post_y %>%
  mutate(when = "Post")

df_5c_prop_y <- union(df_c_pre_y, df_c_post_y) %>% mutate(section = "B")


df_5_y <- union(df_5c_prop_y, df_5b_prop_y)

#plot
 ggplot(df_5_y, aes(x = as.numeric(range), y = value, color = section, linetype = when)) +
  geom_line(size = 1) +
  geom_point(size = 2) + scale_y_continuous(labels = scales::percent_format()) +
     scale_linetype_manual(values=c("solid", "dashed"), labels = c("After", "Before"))+
      scale_color_manual(values=c("#D98E3A", "#A283CD"))+
  labs(x = "Range", y = "Precent")  + theme_light() + labs(color= "Question", linetype= "Before / After", title = "How much do you know about the following topics?", subtitle = "Elementary School\nA. Animals in the school environment\nB. How animals in the school environment affect humans")
 
```



# A graph which shows the middle school rankings for the question "Do you agree with the following sentences?"

```{r}
# For tet
#make numeric
post$five_b <- as.numeric(post$five_b)
post$five_c <- as.numeric(post$five_c)
post$five_d <- as.numeric(post$five_d)



#count 4b
pre_sch_count_4b <- pre %>% filter(class =='tet') %>% drop_na(four_b) %>% count(four_b, name = 'count_4b_pre')
post_sch_count_4b  <- post %>% filter(class =='tet') %>% drop_na(five_b)  %>% count(five_b, name = 'count_4b_post')

## count -> precentage
pre_sch_count_4b$prop_4b_pre <- pre_sch_count_4b$count_4b_pre / sum(pre_sch_count_4b$count_4b_pre)
post_sch_count_4b$prop_4b_post <- post_sch_count_4b$count_4b_post/ sum(post_sch_count_4b$count_4b_post)

#count 4c
pre_sch_count_4c <- pre %>% filter(class =='tet') %>% drop_na(four_c) %>% count(four_c, name = 'count_4c_pre')
post_sch_count_4c  <- post %>% filter(class =='tet') %>% drop_na(five_c) %>% count(five_c, name = 'count_4c_post')

## count -> precentage
pre_sch_count_4c$prop_4c_pre <- pre_sch_count_4c$count_4c_pre / sum(pre_sch_count_4c$count_4c_pre)
post_sch_count_4c$prop_4c_post <- post_sch_count_4c$count_4c_post / sum(post_sch_count_4c$count_4c_post)


#count 4d
pre_sch_count_4d <- pre %>% filter(class =='tet') %>% drop_na(four_d) %>% count(four_d, name = 'count_4d_pre')
post_sch_count_4d  <- post %>% filter(class =='tet') %>% drop_na(five_d) %>% count(five_d, name = 'count_4d_post')


## count -> precentage
pre_sch_count_4d$prop_4d_pre <- pre_sch_count_4d$count_4d_pre / sum(pre_sch_count_4d$count_4d_pre)
post_sch_count_4d$prop_4d_post <- post_sch_count_4d$count_4d_post / sum(post_sch_count_4d$count_4d_post)


## 4B ##

#change col names
colnames(pre_sch_count_4b) <- c("range", "4b_pre", "4b_pre_prop")
colnames(post_sch_count_4b) <- c("range", "4b_post", "4b_post_prop")

#union & change NA to 0
df_4b <- merge(x=pre_sch_count_4b,y=post_sch_count_4b,by=c("range"),all.x =TRUE)

df_4b$`4b_pre`[is.na(df_4b$`4b_pre`)] <- 0
df_4b$`4b_post`[is.na(df_5b$`4b_post`)] <- 0


df_4b_prop <- df_4b %>% select(1,3,5)
df_4b_prop$`4b_pre_prop`[is.na(df_4b_prop$`4b_pre_prop`)] <- 0
df_4b_prop$`4b_post_prop`[is.na(df_4b_prop$`4b_post_prop`)] <- 0

#reshape the data
 df_4b_prop_long <- df_4b_prop %>%
 gather(key = "question", value = "value", -range)


df_b_pre <- filter( df_4b_prop_long, question == "4b_pre_prop")
df_b_pre <- df_b_pre %>%
  mutate(when = "Pre")

df_b_post <- filter( df_4b_prop_long, question == "4b_post_prop")
df_b_post <- df_b_post %>%
  mutate(when = "Post")

df_4b_prop <- union(df_b_pre, df_b_post) %>% mutate(section = "A")
df_4b_prop$range <- as.double(df_4b_prop$range)

## 4C ##

#make numeric
#count 4c
pre_sch_count_4c <- pre %>% filter(class =='tet') %>% drop_na(four_c) %>% count(four_c, name = 'count_4c_pre')
post_sch_count_4c  <- post %>% filter(class =='tet') %>% drop_na(five_c)  %>% count(five_c, name = 'count_4c_post')


## count -> precentage
pre_sch_count_4c$prop_4c_pre <- pre_sch_count_4c$count_4c_pre / sum(pre_sch_count_4c$count_4c_pre)
post_sch_count_4c$prop_4c_post <- post_sch_count_4c$count_4c_post / sum(post_sch_count_4c$count_4c_post)


#change col names
colnames(pre_sch_count_4c) <- c("range", "4c_pre", "4c_pre_prop")
colnames(post_sch_count_4c) <- c("range", "4c_post", "4c_post_prop")

#union & change NA to 0
df_4c <- merge(x=post_sch_count_4c,y=pre_sch_count_4c,by="range",all.x=TRUE)
df_4c$`4c_pre`[is.na(df_4c$`4c_pre`)] <- 0
df_4c$`4c_post`[is.na(df_4c$`4c_post`)] <- 0

df_4c_prop <- df_4c %>% select(1,3,5)
df_4c_prop$`4c_pre_prop`[is.na(df_4c_prop$`4c_pre_prop`)] <- 0
df_4c_prop$`4c_post_prop`[is.na(df_4c_prop$`4c_post_prop`)] <- 0

#reshape the data
 df_4c_prop_long <- df_4c_prop %>%
 gather(key = "question", value = "value", -range)
 
 
df_c_pre <- filter( df_4c_prop_long, question == "4c_pre_prop")
df_c_pre <- df_c_pre %>%
  mutate(when = "Pre")

df_c_post <- filter( df_4c_prop_long, question == "4c_post_prop")
df_c_post <- df_c_post %>%
  mutate(when = "Post")

df_4c_prop <- union(df_c_pre, df_c_post) %>% mutate(section = "B")

## 4D ##

#make numeric
#count 4d
pre_sch_count_4d <- pre %>% filter(class =='tet') %>% drop_na(four_d) %>% count(four_d, name = 'count_4d_pre')
post_sch_count_4d  <- post %>% filter(class =='tet') %>% drop_na(five_d)  %>% count(five_d, name = 'count_4d_post')


## count -> precentage
pre_sch_count_4d$prop_4d_pre <- pre_sch_count_4d$count_4d_pre / sum(pre_sch_count_4d$count_4d_pre)
post_sch_count_4d$prop_4d_post <- post_sch_count_4d$count_4d_post / sum(post_sch_count_4d$count_4d_post)


#change col names
colnames(pre_sch_count_4d) <- c("range", "4d_pre", "4d_pre_prop")
colnames(post_sch_count_4d) <- c("range", "4d_post", "4d_post_prop")

#union & change NA to 0
df_4d <- merge(x=post_sch_count_4d,y=pre_sch_count_4d,by="range",all.x=TRUE)
df_4d$`4d_pre`[is.na(df_4d$`4d_pre`)] <- 0
df_4d$`4d_post`[is.na(df_4d$`4d_post`)] <- 0

df_4d_prop <- df_4d %>% select(1,3,5)
df_4d_prop$`4d_pre_prop`[is.na(df_4d_prop$`4d_pre_prop`)] <- 0
df_4d_prop$`4d_post_prop`[is.na(df_4d_prop$`4d_post_prop`)] <- 0

#reshape the data
 df_4d_prop_long <- df_4d_prop %>%
 gather(key = "question", value = "value", -range)
 
 
df_d_pre <- filter( df_4d_prop_long, question == "4d_pre_prop")
df_d_pre <- df_d_pre %>%
  mutate(when = "Pre")

df_d_post <- filter( df_4d_prop_long, question == "4d_post_prop")
df_d_post <- df_d_post %>%
  mutate(when = "Post")

df_4d_prop <- union(df_d_pre, df_d_post) %>% mutate(section = "C")


#make range col double
df_4c_prop$range <- as.double(df_4c_prop$range)
df_4d_prop$range <- as.double(df_4d_prop$range)
df_4b_prop$range <- as.double(df_4b_prop$range)

df_4b_prop$value <- as.double(df_4b_prop$value)
df_4c_prop$value <- as.double(df_4c_prop$value)
df_4d_prop$value <- as.double(df_4d_prop$value)


## UNION EVERYONE
df_4 <- union(df_4d_prop, df_4b_prop) %>% union(df_4c_prop)

#plot
 ggplot(df_4, aes(x = as.numeric(range), y = value, color = section, linetype = when)) +
  geom_line(size = 1) +
  geom_point(size = 2) + scale_y_continuous(labels = scales::percent_format()) +
     scale_linetype_manual(values=c("solid", "dashed"), labels = c("After", "Before"))+
      scale_color_manual(values=c("#D98E3A", "#A283CD", "#5AD196"))+
  labs(x = "Range", y = "Precent")  + theme_light() + labs(color= "Question", linetype= "Before / After", title = "Do you agree with the following sentences?", subtitle = "Middle School\nA. Its important to learn science  even it is not your occupation\nB. My science knowledge helps me in day-to-day life\nC. Science helps to explain world phenomenons" )
```


# A graph which shows the elementry school rankings for the question "Do you agree with the following sentences?"

```{r}
# For tet
#make numeric
post$five_b <- as.numeric(post$five_b)
post$five_c <- as.numeric(post$five_c)
post$five_d <- as.numeric(post$five_d)



#count 4b
pre_sch_count_4b_y <- pre %>% filter(class !='tet') %>% drop_na(four_b) %>% count(four_b, name = 'count_4b_pre_y')
post_sch_count_4b_y  <- post %>% filter(class !='tet') %>% drop_na(five_b)  %>% count(five_b, name = 'count_4b_post_y')

## count -> precentage

pre_sch_count_4b_y$prop_4b_pre_y <- pre_sch_count_4b_y$count_4b_pre_y / sum(pre_sch_count_4b_y$count_4b_pre_y)
post_sch_count_4b_y$prop_4b_post_y <- post_sch_count_4b_y$count_4b_post_y/ sum(post_sch_count_4b_y$count_4b_post_y)

#count 4c
pre_sch_count_4c_y <- pre %>% filter(class !='tet') %>% drop_na(four_c) %>% count(four_c, name = 'count_4c_pre_y')
post_sch_count_4c_y  <- post %>% filter(class !='tet') %>% drop_na(five_c) %>% count(five_c, name = 'count_4c_post_y')

## count -> precentage
pre_sch_count_4c_y$prop_4c_pre_y <- pre_sch_count_4c_y$count_4c_pre_y / sum(pre_sch_count_4c_y$count_4c_pre_y)
post_sch_count_4c_y$prop_4c_post_y <- post_sch_count_4c_y$count_4c_post_y / sum(post_sch_count_4c_y$count_4c_post_y)


#count 4d
pre_sch_count_4d_y <- pre %>% filter(class !='tet') %>% drop_na(four_d) %>% count(four_d, name = 'count_4d_pre_y')
post_sch_count_4d_y  <- post %>% filter(class !='tet') %>% drop_na(five_d) %>% count(five_d, name = 'count_4d_post_y')


## count -> precentage
pre_sch_count_4d_y$prop_4d_pre_y <- pre_sch_count_4d_y$count_4d_pre_y / sum(pre_sch_count_4d_y$count_4d_pre_y)
post_sch_count_4d_y$prop_4d_post_y <- post_sch_count_4d_y$count_4d_post_y / sum(post_sch_count_4d_y$count_4d_post_y)


## 4B ##

#change col names
colnames(pre_sch_count_4b_y) <- c("range", "4b_pre", "4b_pre_prop")
colnames(post_sch_count_4b_y) <- c("range", "4b_post", "4b_post_prop")

#union & change NA to 0 
df_4b_y <- merge(x=pre_sch_count_4b_y, y=post_sch_count_4b_y, by=c("range"), all.x =TRUE) %>%  slice(1:5)

df_4b_y$`4b_pre`[is.na(df_4b_y$`4b_pre`)] <- 0
df_4b_y$`4b_post`[is.na(df_4b_y$`4b_post`)]<- 0

df_4b_prop_y <- df_4b_y %>% select(1,3,5)
df_4b_prop_y$`4b_pre_prop`[is.na(df_4b_prop_y$`4b_pre_prop`)] <- 0
df_4b_prop_y$`4b_post_prop`[is.na(df_4b_prop_y$`4b_post_prop`)] <- 0

#reshape the data
 df_4b_prop_long_y <- df_4b_prop_y %>%
 gather(key = "question", value = "value", -range)


df_b_pre_y <- filter( df_4b_prop_long_y, question == "4b_pre_prop")
df_b_pre_y <- df_b_pre_y %>%
  mutate(when = "Pre")

df_b_post_y <- filter( df_4b_prop_long_y, question == "4b_post_prop")
df_b_post_y <- df_b_post_y %>%
  mutate(when = "Post")

df_4b_prop_y <- union(df_b_pre_y, df_b_post_y) %>% mutate(section = "A")
df_4b_prop_y$range <- as.double(df_4b_prop_y$range)

## 4C ##

#make numeric
#count 4c
pre_sch_count_4c_y <- pre %>% filter(class !='tet') %>% drop_na(four_c) %>% count(four_c, name = 'count_4c_pre')
post_sch_count_4c_y  <- post %>% filter(class !='tet') %>% drop_na(five_c)  %>% count(five_c, name = 'count_4c_post')


## count -> precentage
pre_sch_count_4c_y$prop_4c_pre <- pre_sch_count_4c_y$count_4c_pre / sum(pre_sch_count_4c_y$count_4c_pre)
post_sch_count_4c_y$prop_4c_post <- post_sch_count_4c_y$count_4c_post / sum(post_sch_count_4c_y$count_4c_post)


#change col names
colnames(pre_sch_count_4c_y) <- c("range", "4c_pre", "4c_pre_prop")
colnames(post_sch_count_4c_y) <- c("range", "4c_post", "4c_post_prop")

#union & change NA to 0 (&remove abstainers)
df_4c_y <- merge(x=pre_sch_count_4c_y,y=post_sch_count_4c_y,by="range",all.x=TRUE) %>%  slice(1:5)
df_4c_y$`4c_pre`[is.na(df_4c_y$`4c_pre`)] <- 0
df_4c_y$`4c_post`[is.na(df_4c_y$`4c_post`)] <- 0

df_4c_prop_y <- df_4c_y %>% select(1,3,5)
df_4c_prop_y$`4c_pre_prop`[is.na(df_4c_prop_y$`4c_pre_prop`)] <- 0
df_4c_prop_y$`4c_post_prop`[is.na(df_4c_prop_y$`4c_post_prop`)] <- 0

#reshape the data
 df_4c_prop_long_y <- df_4c_prop_y %>%
 gather(key = "question", value = "value", -range)
 
 
df_c_pre_y <- filter( df_4c_prop_long_y, question == "4c_pre_prop")
df_c_pre_y <- df_c_pre_y %>%
  mutate(when = "Pre")

df_c_post_y <- filter( df_4c_prop_long_y, question == "4c_post_prop")
df_c_post_y <- df_c_post_y %>%
  mutate(when = "Post")

df_4c_prop_y <- union(df_c_pre_y, df_c_post_y) %>% mutate(section = "B")

## 4D ##

#make numeric
#count 4d
pre_sch_count_4d_y <- pre %>% filter(class !='tet') %>% drop_na(four_d) %>% count(four_d, name = 'count_4d_pre')
post_sch_count_4d_y  <- post %>% filter(class !='tet') %>% drop_na(five_d)  %>% count(five_d, name = 'count_4d_post')


## count -> precentage
pre_sch_count_4d_y$prop_4d_pre <- pre_sch_count_4d_y$count_4d_pre / sum(pre_sch_count_4d_y$count_4d_pre)
post_sch_count_4d_y$prop_4d_post <- post_sch_count_4d_y$count_4d_post / sum(post_sch_count_4d_y$count_4d_post)


#change col names
colnames(pre_sch_count_4d_y) <- c("range", "4d_pre", "4d_pre_prop")
colnames(post_sch_count_4d_y) <- c("range", "4d_post", "4d_post_prop")

#union & change NA to 0
df_4d_y <- merge(x=post_sch_count_4d_y,y=pre_sch_count_4d_y,by="range",all.x=TRUE)
df_4d_y$`4d_pre`[is.na(df_4d_y$`4d_pre`)] <- 0
df_4d_y$`4d_post`[is.na(df_4d_y$`4d_post`)] <- 0

df_4d_prop_y <- df_4d_y %>% select(1,3,5)
df_4d_prop_y$`4d_pre_prop`[is.na(df_4d_prop_y$`4d_pre_prop`)] <- 0
df_4d_prop_y$`4d_post_prop`[is.na(df_4d_prop_y$`4d_post_prop`)] <- 0

#reshape the data
 df_4d_prop_long_y <- df_4d_prop_y %>%
 gather(key = "question", value = "value", -range)
 
 
df_d_pre_y <- filter( df_4d_prop_long_y, question == "4d_pre_prop")
df_d_pre_y <- df_d_pre_y %>%
  mutate(when = "Pre")

df_d_post_y <- filter( df_4d_prop_long_y, question == "4d_post_prop")
df_d_post_y <- df_d_post_y %>%
  mutate(when = "Post")

df_4d_prop_y <- union(df_d_pre_y, df_d_post_y) %>% mutate(section = "C")
df_4c_prop_y$range <- as.double(df_4c_prop_y$range)



## UNION EVERYONE
df_4_y <- union(df_4b_prop_y, df_4c_prop_y) %>% union(df_4d_prop_y)

#plot
 ggplot(df_4_y, aes(x = as.numeric(range), y = value, color = section, linetype = when)) +
  geom_line(size = 1) +
  geom_point(size = 2) + scale_y_continuous(labels = scales::percent_format()) +
     scale_linetype_manual(values=c("solid", "dashed"), labels = c("After", "Before"))+
      scale_color_manual(values=c("#D98E3A", "#A283CD", "#5AD196"))+
  labs(x = "Range", y = "Precent")  + theme_light() + labs(color= "Question", linetype= "Before / After", title = "Do you agree with the following sentences?", subtitle = "Elementary School\nA. Its important to learn science  even it is not your occupation\nB. My science knowledge helps me in day-to-day life\nC. Science helps to explain world phenomenons" )
```

